\documentclass{report}
\title{PROJECT PROPOSAL\\
Customize Movie Database}

\author{1.Iftesam Amin Bhuiyan ID:1621108642\\2.Ibtisum Ahmed Nihal ID:1911638642\\3.Joy Islam ID:2013653642\\Group:3}
\date{11July, 2021}
\begin{document}


\maketitle
\tableofcontents
\newpage
\section{Introduction}
This data base related to art and movies. More or less everyone watch movies to kill their boredom, to watch and learn new things. This database help those user to find new movies like what kind of movie they like. There are a bunch of database like these like imdb.com, rottentomatoes.com and etc but the user have to open 3 or 4 websites to watch movie trailers, Reviews,Cast Crew, Genre, Run-Time, Different Movie Suggestions. So this database project started with the intention of developing a one-stop destination for the user to view all the data. Like
\begin{itemize}
\item User Can Watch Movie Trailers
\item imdb Rating, Rottentomatoes Ratings.
\item User get notified the Release Date of their favorite type of movie. 
\item User Friendly Movie Suggestions
\item Users can watch and give reviews ETC.

\end{itemize}
User can easily get this benefits from this database. 

\section{Object}
\begin{itemize}
\item User Can easily get the movie which they want to watch.
\item User can get to know about the release date of a movie. 
\item User can give reviews and rating about a movie.
\item User can make comment about a movie whether they like the movie or not 
\item This is a Customize Database System. User can log in to their Account and add movies to their Watch list. 

\end{itemize}

\section{Target Users}
\begin{itemize}
\item Users who are trying to find the good movies like their choice can easily through this Database System.  
\end{itemize}

\section{Database Feature and Description}
The web page will open with the user view at first. Anyone who will log in with their User Name and Password Can get into in this Database System. 
Once an user access with their necessary information they can:
\begin{itemize}
\item Watch the upcoming movie list. 
\item Can follow friends and see their watch list and grind new movies. 
\item Give Reviews about Movies. 

\item Notification for Movie Related News.  
\end{itemize}

\section{Tools and Resources}
\begin{itemize}
\item HTML
\item JAVASCRIPT
\item MySQL
\item PHP
\item Web Server
\item XAMPP
\end{itemize}

\section{Benefits}
More or less we all watch movies to enjoy our free time or learn about something different.Many of us using three or four sites to get all information together. But in this Database the user can avoid all hustle to get the desire information together. User can make their personal Watch list and follow other user's watch list so that they can get to know about more films and 
User can also give us feedback to improve the Database more properly. 

\newpage
\section{CHALLENGE}
As we all know, this will be a big Database system and we have to keep it in updating frequently. SO, Cost will be the thing for us. Users have to present with their proper information and we have to keep digging if the user provide the authentic information or not. Lastly, it would be difficult for us to maintain this Database but not impossible,  obviously.  
\end{document}






